---
title: "Bryce Turner's resume"
author:  Bryce Turner
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---


```{r sourceClassesAndFunction, echo = FALSE, message = FALSE, warning=FALSE}
setwd("~/personal/resume/")

library(readxl)
library(tidyverse)

source("sourceScripts/EducationDetails.R")

# Helpful Tools
# https://towardsdatascience.com/create-your-resume-with-pagedown-package-in-r-123ca6310d52

# https://livefreeordichotomize.com/2019/09/04/building_a_data_driven_cv_with_r/
```


```{r prepEducationResumeDetails, echo = FALSE}
educationDetailsDataframe <- read_excel(path = "resume_details.xlsx",
                               sheet = "EducationDetails") %>% 
  arrange(!is.na(EndDate),-EndDate)


allEducationDetails <- mapply(FUN = createEducationDetailFromExcel,
                              rowNum = seq(1, nrow(educationDetailsDataframe)),
                              MoreArgs = list(dataframe = educationDetailsDataframe),
                              SIMPLIFY = TRUE)

allEducationDetails <- lapply(X = allEducationDetails,
                              FUN = renderEducationDetailsForResume) %>% 
  unlist

```

Aside
================================================================================


<!-- ![Lijia Yu](https://avatars1.githubusercontent.com/u/895125?s=400&v=4){width=80%} --->


Contact Info {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> `r "current_email" `
- <i class="fa fa-github"></i> [github.com/yulijia](https://github.com/yulijia)
- <i class="fa fa-phone"></i> `r "current_phone"`



Skills {#skills}
--------------------------------------------------------------------------------

- Experienced in statistical analysis, statistical learning models, and optimization methods.

- Full experience with next generation sequencing data analysis.

- Highly skilled in R, Bash, Perl, Python, LaTeX


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.



Main
================================================================================

Bryce Turner {#title}
--------------------------------------------------------------------------------

Education {data-icon=none data-concise=true}
--------------------------------------------------------------------------------
```{r, echo = FALSE, results='asis'}
cat(allEducationDetails, sep = "\n\n")
```


Research Experience {data-icon=none}
--------------------------------------------------------------------------------

### Graduate Research Assistant

Beijing Institute of Genomics, Chinese Academy of Sciences

Beijing, China

2011 - 2014

- Performed computational biology research towards understanding regulation of alternative splicing in human and mouse transcriptome.
- Found EGFR pathway related mutations, aimed to understand the impacts of cancer mutations on EGFR signaling pathway.

### Bioinformatican

My Health Gene Technology Co., Ltd.

Beijing, China

2015 - 2016

- Investigated how cancer cells spread to other parts of the body at the single cell level.

### Visiting Scientist

University of Alabama at Birmingham

AL, USA

2016 - 2018

- Investigated the role of mitochondria in development of cancer.
- Investigated the evolution of genome architecture and its role in important evolutionary events.
- Detected thrombotic thrombocytopenic purpura related mutations in mutiple patients' blood genome.
  

Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Data Scientist, intern

SupStat Inc.

Beijing, China

2014

::: concise
- Taught R language to beginners. 
- Wrote Shiny app demos.
- Converted statistical tutorials from SPSS to R language.
:::

### Bioinformatician

My Health Gene Technology Co., Ltd.

Beijing, China

2015 - 2016

::: concise
- Analyzed whole-exome sequencing data. 
- Wrote analysis pipelines of ChIP-seq, single cell DNA-seq and single cell RNA-seq.
- Studied tumor metastasis and wrote research reports. 
- Also did case studies to identify the genetic defect causing rare disease.
:::


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

### Introduction to R Language for Beginners.

Instructor of R and Data Mining Training Courses at SupStat Inc.

Beijing, China

2014

### Computational Biology and Bioinformatics.

Teaching assistant of GBS CB2-201 courses at UAB

AL, USA

2016 - 2017


Selected Publications and Posters {data-icon=file}
--------------------------------------------------------------------------------

### Genetic and epigenetic signals are found predictive to the distribution of intra-individual divergence of alternative splicing.

Poster for 2013 International Conference of Genomics

Qingdao, China

2014

**Yu L**, Chen B, Zhang Z.

### ESCRT-0 complex modulates Rbf mutant cell survival by regulating Rhomboid endosomal trafficking and EGFR signaling.

J Cell Sci. 2016 May 15;129(10):2075-84.

N/A

2016 

Sheng Z, **Yu L**, Zhang T, Pei X, Li X, Zhang Z and Du W. 
