%----------------------------------------------------------------------------------------
%   Bryce Turner's Resume
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default document font size

 %\input{BryceTurner_cv_structure.tex} % Include the file specifying the document structure and styling

% Set PDF meta-information
%\hypersetup{
%	pdftitle={Bryce Turner - Resume},
%	pdfauthor={Bryce Turner}
%}

%----------------------------------------------------------------------------------------
\begin{document}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
% HEADING AND PERSONAL DETAILS
%----------------------------------------------------------------------------------------

\begin{center}
{\LARGE\bfseries Bryce C. Turner} \\% Name
\emph{Senior Research Assistant} {\textbullet} Federal Reserve Board (Remote) {\textbullet} Boston, MA\\

Phone: 203-524-2090 {\textbullet} Email: \href{mailto: BCTurner20@gmail.com}{B.C.Turner20@gmail.com}  {\textbullet}   Citizenship: USA \\ 
\end{center}

\smallskip

%----------------------------------------------------------------------------------------
%  SUMMARY
%----------------------------------------------------------------------------------------
\smallskip
\MakeUppercase{\bf Summary}
\smallskip
\hrule
\smallskip
\begin{itemize}[topsep=3pt,itemsep= 2pt,partopsep=0pt, parsep= 0pt, leftmargin = *]
\item[] Detailed analyst with over 2 years of experience developing public databases, anticipating problems and implementing fixes before systems fail. Creative thinker with over 3 years testing hypotheses and telling stories using statistical analysis and econometrics.
\end{itemize}
%----------------------------------------------------------------------------------------
%  EXPERIENCE
%----------------------------------------------------------------------------------------

\MakeUppercase{\bf Experience}
\smallskip
\hrule
% 
% What is my story here:
    % Extensive data experience, utilizing both micro and macro economic experience, coupled with a demonstrated ability to communicate my findings to a wide variety of audiences
% Major Initiatives
   % 529 Plans -> Less important
   % Bonds to Market-Value via NAIC Data - R Functions
      % Insurance Trading of Cat Bonds & Insurance Holdings by Geography -> Follow on projects that have been made possible by me
   % Banks, Nonbanks, Mon Pol -> Curiosity, Self-starter, Ownership
   % Reinsurance
   % CLOs in the Accounts -> Trans-organization communication and confirmations
   % 
% Current Initiatives

\begin{itemize}[topsep=3pt,itemsep= 2pt,partopsep=0pt, parsep= 0pt, leftmargin = *]
	\item[]   {\bf Federal Reserve Board of Governors} \hfill{Washington, DC} \\ 
			\emph{Senior Research Assistant} {\textbullet} Flow of Funds Section \hfill {March 2018 - Present} 
		\begin{itemize}  [topsep=1pt,itemsep= 3pt,partopsep=0pt, parsep= 0pt, leftmargin = *] 
			\item Developed, streamlined, and overhauled data processes for Financial Accounts of the United States and other public-facing projects. Proposed and implemented process changes and new data sources to increase accuracy. Enhanced knowledge of several statistical languages, especially R.  
			\item Collaborated across Federal Reserve System to develop materials for Board Briefings, Internal Presentations, and ad-hoc Policy Projects. Presented results orally and in writing. 
			\item Explored new research initiatives, spearheaded important analyses, and co-authored two academic papers.
			\item[] {\bf Major Projects}
			\begin{itemize} [topsep=2pt,itemsep= 3pt,partopsep=0pt, parsep= 0pt, leftmargin = *]
					\item[] {\bf CLOs in the Financial Accounts} Examined and verified conflicting data sources to understand market size. Organized and presented findings for internal dissemination.
					\item[] {\bf Monetary Policy Research Paper} Expanded existing project to measure Mortgage Lenders' responses to Monetary Policy, demonstrating self-motivation and creativity. Spearheaded analysis and created visualizations for use in paper and presentations. Strengthened knowledge of econometric techniques.
					\item[] {\bf Wealth Effect Research Paper} Designed creative econometric technique to study effect of wealth on productivity. Collaborated with co-author to verify findings, display results, and write sections of paper.
					\item[] {\bf Conversion of Insurance Bond Holdings} Converted Insurance Bond Holdings from Book Value to Market Value. Developed flexible tools in R to reliably extract information from messy underlying data sources. Enhanced subsequent projects by increasing usability of data source.
					\item[] {\bf Section 529 Plans} Overhauled process for calculating and presenting of Section 529 Plan assets. Saved dozens of man-hours per year and increased process reliability.  Learned regular expressions in R.
					% 
			\end{itemize}
		\end{itemize}
		
	\item[]   {\bf The Stanton Foundation} \hfill{Cambridge, MA} \\ 
			\emph{Program Analyst} 	 \hfill {January 2017 - August 2017} 	
		\begin{itemize}  [topsep=1pt,itemsep= 3pt,partopsep=0pt, parsep= 0pt, leftmargin = *] 

			\item Constructed data pipeline to oversee and evaluate grant program distributing over \$1M. Published results in K9 Cop Magazine and penned memo to Board  on cost-efficiency and viability of program.
			\item Examined empirical literature on Discount Factors in Private Equity Valuations.  Presented findings in writing and in person to Board of Directors and Outside Counsel.
        	\end{itemize}
        	\item[]   {\bf Wayfair, Inc.} \hfill{Boston, MA} \\ 
        	\emph{Claims and Logistics Co-Op} 	 \hfill {January 2015 - June 2015} 
\end{itemize}
%----------------------------------------------------------------------------------------
%  TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\smallskip
\MakeUppercase{\bf Technical Skills}
\smallskip
\hrule

\begin{itemize}[topsep=3pt,itemsep= 2pt,partopsep=0pt, parsep= 0pt, leftmargin = *]
	\item[]  Advanced R, Advanced Stata, Advanced Excel, Intermediate {\LaTeX}, Intermediate Python,  Intermediate SQL
\end{itemize}
%----------------------------------------------------------------------------------------
%  PRESENTATIONS
%----------------------------------------------------------------------------------------
\smallskip
\MakeUppercase{\bf Presentations}
\smallskip
\hrule

\begin{itemize}[topsep=3pt,itemsep= 2pt,partopsep=0pt, parsep= 0pt, leftmargin = *]
	\item[]  {\bf CLOs in the Financial Accounts } \hfill {May 2019} \\
			\emph{Federal Reserve Board} {\textbullet} with Youngsuk Yook
	\item[]  {\bf Discount Factors in Private Equity Valuations} \hfill {June 2017} \\
			\emph{The Stanton Foundation Board of Directors} 
\end{itemize}


%----------------------------------------------------------------------------------------
%  PAPERS AND PUBLICATIONS
%----------------------------------------------------------------------------------------
\smallskip
\MakeUppercase{\bf Papers and Publications}
\smallskip
\hrule
	\begin{itemize}  [topsep=3pt,itemsep= 2pt,partopsep=2pt, parsep= 2pt, leftmargin = *]
		\item[] \emph{Nonbanks, Banks, and Monetary Policy: U.S. Loan-Level Evidence since the 1990s} \\ (with David Elliott, Ralf R. Meisenzahl and Jos\'e-Luis Peydr\'o)
		\item[] \emph{A Stroke of Luck: Estimating the Effect of Wealth on Worker Productivity} \\ (with Joseph Briggs)
		\item[] \emph{The Cost of Operating a K9 Unit}, K9 Cop Magazine, Summer 2017 Edition
	\end{itemize}

%----------------------------------------------------------------------------------------
%  EDUCATION
%----------------------------------------------------------------------------------------
\MakeUppercase{\bf Education}
\smallskip
\hrule
\begin{itemize}[topsep=3pt,itemsep= 2pt,partopsep=0pt, parsep= 0pt, leftmargin = *]
	\item[] {\bf Northeastern University} \hfill {December 2017}\\
    \emph{B.S. in Economics} {\textbullet} \emph{Minor in Mathematics} \hfill {\emph{Cum Laude}} 
\end{itemize}

%----------------------------------------------------------------------------------------
%  OTHER
%----------------------------------------------------------------------------------------
%\MakeUppercase{\bf Other}
%\smallskip
%\hrule
%\begin{itemize}[topsep=3pt,itemsep= 2pt,partopsep=0pt, parsep= 0pt, leftmargin = *]
%	\item[] {Positive Adjudication of a Tier-4 Background Check from The US Office of Personnel Management}\\
%\end{itemize}

\pagenumbering{gobble}  %To suppress page numbering

\end{document}